%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {\small Software Developer} % Job title
  {\normalsize Shopify} % Organization
  {\small Montreal, Quebec, Canada} % Location
  {\small May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item \small Contributed a number of new user-facing features as well as large refactors to Shopify's core platform.
      \item \small Played a significant role as a technical domain expert for multiple projects in the Domains \& SSL team's ongoing roadmap.
      \item \small Developed maintanable code with performance in mind as part of one of the world's largest Ruby on Rails codebases.
      \item \small Participated in the organization's test-driven development approach to continuous integration and deployment.
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{-18mm}
  \cventry
  {} % Job title
  {} % Organization
  {} % Location
  {\small May. 2017 - Aug. 2017 } % Date(s)
    {
    }
%---------------------------------------------------------
\vspace{11mm}
  \cventry
  {\small Technical Operations \& Service Automation Developer} % Job title
  {\normalsize AppDirect} % Organization
  {\small Montreal, Quebec, Canada} % Location
  {\small Sept. 2017 - Apr. 2018 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item \small Created a continuous integration pipeline for complex infrastructure components which supported the business.
      \item \small Standardized continuous integration and delivery principles to enable large platform changes with no service outages.
      \item \small Leveraged a variety of technologies such as Docker, Terraform, Packer, Salt, Ansible, and cloud platforms like AWS.
      \item \small Developed a variety of unit and integration tests to query the state of infrastructure once operations had been applied
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {\small Web Application Developer} % Job title
  {\normalsize AppHelp by AppDirect} % Organization
  {\small Montreal, Quebec, Canada} % Location
  {\small Sept. 2015 - Apr. 2017 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item \small Developed web applications with technologies like Javascript, React, Redux, AngularJS, Node.js, Python, Scala, C++ and more.
      \item \small Consistently applied a test-driven development (TDD) and agile approach in order to maintain complex software systems.
      \item \small Successfully led the development and delivery of user-facing projects with changing requirements and shifting deadlines.
      \item \small Took part in the organization's processes, code reviews, project demos, lunch \& learns, hackathons and more.
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{2mm}
  \cventry
  {\small Web Developer and Team Advisor} % Job title
  {\normalsize Concordia University} % Organization
    {\small Montreal, Quebec, Canada} % Location
    {\small May 2014 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item \small Designed and developed a team project wiki with technologies like Javascript, jQuery, CSS and MediaWiki.
      \item \small Excelled in a leadership role as a part of the Science and Engineering team.
      \item \small Received a silver medal at the International Genetically Engineered Machine competition our research in biotechnology.
      \end{cvitems}
    }
\end{cventries}
